Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-08 article.rnw
Move code for the figures into the article-analysis script.

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		hist(brute_data$statistics[[ic]],
			main="",
			xlab=ic_name,
			xaxs='i',
			yaxs='i',
			ylim=c(0,6000)
		)
		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="purple")
	@
	\end{subfigure}

@@

	<<>>=
		best_model_index <- which.max(brute_data$statistics[[ic_weight]])
		best_row_grouping <- brute_data$get_row_grouping(best_model_index)
		best_col_grouping <- brute_data$get_col_grouping(best_model_index)
		best_alpha_matrix <- brute_data$parameters[[best_model_index]]$alpha_values

		ordering <- get_ordering(list(best_row_grouping, best_col_grouping))
		best_species_names <- brute_data$species_names[ordering]
		best_row_grouping <- best_row_grouping[ordering]
		best_col_grouping <- best_col_grouping[ordering]
		best_alpha_matrix <- best_alpha_matrix[ordering,ordering]

		best_row_coclassification <- as_coclassification_matrix(best_row_grouping)
		best_col_coclassification <- as_coclassification_matrix(best_col_grouping)
	@

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			grouped_alpha_matrix(
				best_species_names,
				best_row_grouping,
				best_col_grouping,
				best_alpha_matrix
			)
		@
		\caption{Grouped alpha matrix}
		\label{fig:best-alpha-matrix}
	\end{subfigure}

@@

	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_col_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive effects\\(columns)}
		\label{fig:best-coclassification-cols}
	\end{subfigure}
	%
	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			minimal_coclassification_kable(
				best_row_coclassification,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive responses\\(rows)}
		\label{fig:best-coclassification-rows}
	\end{subfigure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			weighted_coclassification_kable(
				weighted_col_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive effects}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			weighted_coclassification_kable(
				weighted_row_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Coclassification of competitive responses}
		\label{fig:coclassification-rows}
	\end{subfigure}

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		ic_histogram(brute_data)
	@
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			cat(best_model_output_table$grouped_alpha_matrix)
		@
		\caption{Grouped alpha matrix}
		\label{fig:best-alpha-matrix}
	\end{subfigure}

@@

	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			cat(best_model_output_table$row_coclassification_table)
		@
		\caption{Coclassification of competitive effects\\(columns)}
		\label{fig:best-coclassification-cols}
	\end{subfigure}
	%
	\begin{subfigure}{0.49\textwidth}
		\centering
		<<>>=
			cat(best_model_output_table$row_coclassification_table)
		@
		\caption{Coclassification of competitive responses\\(rows)}
		\label{fig:best-coclassification-rows}
	\end{subfigure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			cat(weighted_coclassification_matrices$col)
		@
		\caption{Coclassification of competitive effects}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<>>=
			cat(weighted_coclassification_matrices$row)
		@
		\caption{Coclassification of competitive responses}
		\label{fig:coclassification-rows}
	\end{subfigure}

### 2022-08-08 supp.rnw
Move code for the figures into the article-analysis script.

<<echo=FALSE>>=
	order_species <- function(vec, names, order) {
		factor(vec, levels = names[order])
	}

	model_fit_plot <- function(parameters, species_output_order) {
		plot_df <- data.frame(
			observed = input_data$response_vector,
			fitted = input_data$get_fitted_values(parameters),
			focal = species_dat$name[input_data$focal_vector]
		)

		plot_df$focal <- order_species(plot_df$focal, species_dat$name, species_output_order)

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(slope = 1, intercept = 0) +
			ggplot2::facet_wrap(.~focal) +
			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Predicted growth rate (per capita)")
		return(plot)
	}

	partial_residual_plot <- function(parameters, species_output_order) {
		plot_df <- c()
		for(row_index in 1:num_species) {
			for(col_index in 1:num_species) {
				temp_df <- data.frame(
					y = input_data$get_partial_residuals(parameters, row_index, col_index),
					x = input_data$get_partial_residuals_x(row_index, col_index)
				)
				temp_df$row_index <- rep(row_index, nrow(temp_df))
				temp_df$col_index <- rep(col_index, nrow(temp_df))
				temp_df$alpha <- parameters$alpha_values[row_index, col_index]
				plot_df <- rbind(plot_df, temp_df)
			}
		}

		plot_df$row_species <- species_dat$name[plot_df$row_index]
		plot_df$col_species <- species_dat$name[plot_df$col_index]
		plot_df$row_species <- order_species(plot_df$row_species, species_dat$name, species_output_order)
		plot_df$col_species <- order_species(plot_df$col_species, species_dat$name, species_output_order)

		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
			ggplot2::geom_point() +
			ggplot2::geom_smooth(method = lm, formula = y~x) +
			ggplot2::geom_abline(ggplot2::aes(slope = alpha, intercept = 0)) +
			ggplot2::facet_grid(row_species~col_species) +
			ggplot2::labs(x = "Number of individuals of competing species", y = "Partial residual growth rate of focal species (per capita)") +
			ggplot2::theme(strip.text = ggplot2::element_text(size=7))
		return(plot)
	}

	best_parameters <- brute_data$parameters[[which.max(brute_data$statistics[[ic_weight]])]]
	average_parameters <- brute_data$average_parameters
@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(best_parameters, species_output_order))
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(model_fit_plot(average_parameters, species_output_order))
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residual_plot(best_parameters, species_output_order))
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(partial_residual_plot(average_parameters, species_output_order))
	@

>>>>

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(best_model_fit_plot)
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(average_model_fit_plot)
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(best_partial_residual_plot)
	@

@@

\begin{figure}
	<<echo=FALSE>>=
		plot(average_partial_residual_plot)
	@
